Doing Better Than UCT: Rational Monte Carlo Sampling in Trees

### 2011-06-21 paper/rmcts/paper.tex
paper in progress

@@

{\bf Chernoff bound:} for $m$ independent random variables $X_1, X_2, ..., X_m$
taking values 0 or 1, $X=\sum_{i=1}^m X_i$, and $0\le\delta\le 1$:

@@

>>>>

$\hat{C}_f$

@@

{\bf Chernoff bound (see \cite{Hagerup.chernoff}):} for $m$ independent random variables $X_1, X_2, ..., X_m$
taking values 0 or 1, $X=\sum_{i=1}^m X_i$, and $0\le\delta\le 1$:

@@

For an analysis of pure exploration of uniform and UCB algorithms, see also
\cite{Bubeck.pure}.
